---
title: "Senior Theses"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```

## Case study: senior theses

```{r echo = TRUE}
theses <- read.csv("sample-theses.csv")
str(theses)
```


## {.build .smaller}

**Question 1**: What is the average number of times a thesis is checked out?

```{r, fig.height=3, fig.width=5, fig.align='center'}
ggplot(theses, aes(x = checkouts)) +
  geom_bar()
```

```{r}
theses %>%
  summarize(mean(checkouts),
            median(checkouts))
```

## {.build}

**Question 1**: What is the average number of times a thesis is checked out?

**Confidence interval on one mean **

$$
\bar{x} \pm t^* \times s/\sqrt n
$$

```{r}
stats <- theses %>%
  summarize(n     = n(),
            x_bar = mean(checkouts),
            s     = sd(checkouts))
stats$x_bar + c(1, -1) * qt(.025, df = stats$n - 1) * stats$s / stats$n
```


## {.build .smaller}

**Question 2**: Is the distribution of theses uniform in time?

```{r}
ggplot(theses, aes(x = year)) +
  geom_histogram()
```


## {.build .smaller}

**Question 2**: Is the distribution of theses uniform in time?

**Chi-squared goodness of fit test **

```{r, fig.width=7, fig.height=4, eval = FALSE}
bd <- data.frame(year_binned = cut(theses$year, 
                                            seq(from = 1920, to = 2020, by = 10)))
ggplot(bd, aes(x = year_binned)) +
  geom_bar() +
  geom_hline(yintercept = stats$n/10, 
             color = "goldenrod")
```

## {.smaller}

**Question 2**: Is the distribution of theses uniform in time?

**Chi-squared goodness of fit test **

```{r, fig.width=7, fig.height=4, echo = FALSE}
bd <- data.frame(year_binned = cut(theses$year, 
                                            seq(from = 1920, to = 2020, by = 10)))
ggplot(bd, aes(x = year_binned)) +
  geom_bar() +
  geom_hline(yintercept = stats$n/10, 
             color = "goldenrod")
```

## {.build .smaller}

**Question 2**: Is the distribution of theses uniform in time?

**Chi-squared goodness of fit test **

```{r}
(obs <- table(bd$year_binned))
```

```{r}
(exp <- length(bd$year_binned)/10)
```

```{r}
(chisq_obs <- sum((obs - exp)^2/exp))
```

## {.build .smaller}

**Question 2**: Is the distribution of theses uniform in time?

**Chi-squared goodness of fit test **

```{r}
pchisq(chisq_obs, df = length(obs) - 1, lower.tail = FALSE)
```


## {.build .smaller}

**Question 3**: What is the relationship between the age of a thesis and the number of checkouts?

```{r}
head(theses)
theses <- theses %>%
  mutate(age = 2017 - year)
head(theses)
```

## {.build .smaller}

**Question 3**: What is the relationship between the age of a thesis and the number of checkouts?

```{r}
ggplot(theses, aes(x = age, y = checkouts)) +
  geom_jitter()
```

## {.build .smaller}

**Question 3**: What is the relationship between the age of a thesis and the number of checkouts?

```{r}
m1 <- lm(checkouts ~ age, data = theses)
summary(m1)
```

## {.build .smaller}

**Question 3**: What is the relationship between the age of a thesis and the number of checkouts?

```{r}
ggplot(theses, aes(x = age, y = checkouts)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE)
```


#



## Poisson Regression {.build .smaller}

```{r}
m2 <- glm(checkouts ~ age, data = theses, family = "poisson")
summary(m2)
```

## {.build .smaller}

```{r}
ggplot(theses, aes(x = age, y = checkouts)) +
  geom_jitter() +
  stat_function(fun = function(age) {exp(coef(m2)[1] + coef(m2)[2] * age)},
                color = "red")
```

## {.build .smaller}

```{r}
t2 <- theses %>%
  filter(year > 1994)
m2 <- glm(checkouts ~ age, data = t2, family = "poisson")
summary(m2)
```

## {.build .smaller}

```{r}
qplot(x = age, y = checkouts, data = t2, geom = "jitter") +
  stat_function(fun = function(age) {exp(coef(m2)[1] + coef(m2)[2] * age)},
                color = "red")
```



# Ground truth

## From the library's database...{.build .smaller}

```{r}
theses_lib <- read.csv("library_theses_data.csv")
head(theses_lib)
```

## {.build .smaller}

**Question 1**: What is the average number of times a thesis is checked out?

```{r, fig.height=3, fig.width=5, fig.align='center'}
qplot(x = checkouts, data = theses_lib, geom = "bar")
```

```{r}
theses_lib %>%
  summarize(mean(checkouts),
            median(checkouts))
```

## {.build .smaller}

**Question 2**: Is the distribution of theses uniform in time?

```{r}
qplot(x = year, data = theses_lib, geom = "histogram")
```

## {.build .smaller}

**Question 3**: What is the relationship between the age of a thesis and the number of checkouts?

```{r}
theses_lib <- theses_lib %>%
  mutate(age = 2017 - year)
qplot(x = age, y = checkouts, data = theses_lib, geom = "jitter")
```



## Poisson Regression {.build .smaller}

```{r}
t3 <- theses_lib %>%
  filter(year > 1994)
m3 <- glm(checkouts ~ age, data = t3, family = "poisson")
summary(m3)
```

## {.build .smaller}

```{r}
qplot(x = age, y = checkouts, data = t3, geom = "jitter") +
  stat_function(fun = function(age) {exp(coef(m3)[1] + coef(m3)[2] * age)},
                color = "red")
```

## How'd we do?

```{r}
coef(m2) # our data
coef(m3) # library's data
```


