---
title: "Inference for categorical data"
output:
  html_document:
    css: ../lab.css
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, message = FALSE, warning = FALSE)
```

In August of 2012, news outlets ranging from the [Washington Post](http://www.washingtonpost.com/national/on-faith/poll-shows-atheism-on-the-rise-in-the-us/2012/08/13/90020fd6-e57d-11e1-9739-eef99c5fb285_story.html) to the [Huffington Post](http://www.huffingtonpost.com/2012/08/14/atheism-rise-religiosity-decline-in-america_n_1777031.html) ran a story about the rise of atheism in America. The source for the story was a poll that asked people, "Irrespective of whether you attend a place of worship or not, would you say you are a religious person, not a religious person or a convinced atheist?" This type of question, which asks people to classify themselves in one way or another, is common in polling and generates categorical data. In this lab we take a look at the atheism survey and explore what's at play when making inference about population proportions using categorical data.

## Getting Started

### Load packages

In this lab we will explore the data using the `dplyr` package and visualize it 
using the `ggplot2` package for data visualization. The data can be found in the
companion package for OpenIntro labs, `oilabs`.

Let's load the packages.

```{r load-packages, message=FALSE, eval=TRUE}
library(tidyverse)
library(oilabs)
library(infer)
```

### The survey

The press release for the poll, conducted by WIN-Gallup International, can be accessed [here](http://www.wingia.com/web/files/richeditor/filemanager/Global_INDEX_of_Religiosity_and_Atheism_PR__6.pdf).

Take a moment to review the report then address the following questions.

1.  In the first paragraph, several key findings are reported. Do these 
    percentages appear to be *sample statistics* (derived from the data 
    sample) or *population parameters*? Explain your reasoning.

2.  The title of the report is "Global Index of Religiosity and Atheism". To
    generalize the report's findings to the global human population, what must 
    we assume about the sampling method? Does that seem like a reasonable 
    assumption?

### The data

Turn your attention to Table 6 (pages 15 and 16), which reports the
sample size and response percentages for all 57 countries. While this is
a useful format to summarize the data, we will base our analysis on the
original data set of individual responses to the survey. Load this data
set into R with the following command.

```{r head-data}
data(atheism)
```

3.   What does each row of Table 6 correspond to? What does each row of 
    `atheism` correspond to?

To investigate the link between these two ways of organizing this data, take a 
look at the estimated proportion of atheists in the United States. Towards 
the bottom of Table 6, we see that this is 5%. We should be able to come to 
the same number using the `atheism` data.

4.  Using the command below, create a new dataframe called `us12` that contains
    only the rows in `atheism` associated with respondents to the 2012 survey 
    from the United States. Next, calculate the proportion of atheist 
    responses. Does it agree with the percentage in Table 6? If not, why?

```{r us-atheism}
us12 <- atheism %>%
  filter(nationality == "United States", year == "2012")
```

## Inference on proportions

As was hinted earlier, Table 6 provides *statistics*, that is, 
calculations made from the sample of 51,927 people. What we'd like, though, is 
insight into the population *parameters*. You answer the question, "What 
proportion of people in your sample reported being atheists?" with a 
statistic; while the question "What proportion of people on earth would report 
being atheists" is answered with an estimate of the parameter.

### Normal Theory

The traditional method of calculating a confidence interval approximates the sampling distribution by using the Normal distribution.

5.  Write out the conditions for using the Normal distribution to construct a 95% confidence
    interval for the proportion of atheists in the United States in 2012.
    Are you confident all conditions are met?

If the conditions for inference are reasonable, we can trust that the Normal curve provides a reasonably good approximation. Let's proceed with calculating a traditional 95% confidence interval.

```{r eval = FALSE}
n      <- 
p_hat  <- 
SE     <-
z_star <- qnorm(    )
MoE    <- 
c(p_hat - MoE, p_hat + MoE)
```

6.   Please fill out the remaining code in the chunk above to walk through the steps of 
     calculating a confidence interval. `z_star` is the number of standard errors that we'll
     be going out to capture 95% of the sampling distribution. This number should be around
     1.96, but you can be more precise by using the `qnorm()` function.
     
```{r eval = FALSE, echo = FALSE}
n      <- nrow(us12)
p_hat  <- us12 %>%
  summarize(mean(response == "atheist")) %>%
  pull()
SE     <- sqrt(p_hat*(1 - p_hat)/n)
z_star <- qnorm(.975)
MoE    <- z_star * SE
c(p_hat - MoE, p_hat + MoE)
```


### Bootstrap SE

We've seen how the bootstrap can provide an alternate path to estimating the standard error needed for our confidence interval. Let's compare to see how different the two methods are.

7.   Use `infer` to calculate the a bootstrap estimate of the standard error (that is, the standard deviation of the bootstrap distribution). Use this estimate to recompute the margin of error and the resulting confidence interval. Was it the same as or similar to your Normal theory approach?


```{r eval = FALSE, echo = FALSE}
SE <- us12 %>%
  specify(response = response) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop", success = "atheist") %>%
  summarize(se = sd(stat)) %>%
  pull()

MoE    <- z_star * SE
c(p_hat - MoE, p_hat + MoE)
```

7.  Using *both* the Normal approximation approach and the bootstrap approach, calculate confidence intervals for the 
    proportion of atheists in 2012 in one other country of your choice. Be sure to note whether the 
    conditions for inference are met, and interpet the interval in context of the data.

## How does the proportion affect the margin of error?

Imagine you've set out to survey 1000 people on two questions: are you female? 
and are you left-handed? Since both of these sample proportions were 
calculated from the same sample size, they should have the same margin of 
error, right? Wrong! While the margin of error does change with sample size, 
it is also affected by the proportion.

Think back to the formula for the standard error: $SE = \sqrt{p(1-p)/n}$. This 
is then used in the formula for the margin of error for a 95% confidence 
interval: $ME = 1.96\times SE = 1.96\times\sqrt{p(1-p)/n}$. Since the 
population proportion $p$ is in this $ME$ formula, it should make sense that 
the margin of error is in some way dependent on the population proportion. We 
can visualize this relationship by creating a plot of $ME$ vs. $p$.

Since sample size is irrelevant to this discussion, let's just set it to
some value ($n = 1000$) and use this value in the following calculations:

```{r n-for-me-plot}
n <- 1000
```

The first step is to make a variable `p` that is a sequence from 0 to 1 with 
each number incremented by 0.01. We can then create a vector of the margin of 
error (`me`) associated with each of these values of `p` using the familiar 
approximate formula ($ME = 2 \times SE$).

```{r p-me}
p <- seq(0, 1, 0.01)
me <- 2 * sqrt(p * (1 - p)/n)
```

Lastly, we plot the two vectors against each other to reveal their relationship.
To do so, we need to first put these variables in a data frame that we can
call in the `ggplot` function.

```{r me-plot}
dd <- data.frame(p = p, me = me)
```

8.  Use `ggplot` to visualize the relationship between the `Population Proportion` and the `Margin of Error` (You can use either `geom_point` or `geom_path` and please add axis labels. Based on this plot, describe the relationship between `p` and `me`. For a given sample size, for which value of `p` is margin of error maximized?

```{r eval = FALSE, echo = FALSE}
ggplot(dd, aes(x = p, y = me)) +
  geom_path(col = "orchid") +
  ylab("Margin of Error") +
  xlab("Population Proportion")
```



* * *

## More Practice

The question of atheism was asked by WIN-Gallup International in a similar 
survey that was conducted in 2005. (We assume here that sample sizes have 
remained the same.) Table 4 on page 13 of the report summarizes survey results 
from 2005 and 2012 for 39 countries. For the following questions, you may use either the Normal theory approach or the computational approach.

13.   Is there convincing evidence that Spain has seen a change in its atheism index 
    between 2005 and 2012? As always, write out the hypotheses for any tests you 
    conduct and outline the status of the conditions for inference. If you find a 
    significant difference, also quantify this difference with a confidence interval. \

14.   Is there convincing evidence that the US has seen a change in its atheism index 
    between 2005 and 2012? As always, write out the hypotheses for any tests you 
    conduct and outline the status of the conditions for inference. If you find a 
    significant difference, also quantify this difference with a confidence interval.

15.   If in fact there has been *no change* in the atheism index in the countries 
    listed in Table 4, in how many of those countries would you expect to 
    detect a change (at a significance level of 0.05) simply by chance?\
    *Hint:* Review the definition of the Type 1 error.

16.   Suppose you're hired by the local government to estimate the proportion of 
    residents that attend a religious service on a weekly basis. According to 
    the guidelines, the estimate must have a margin of error no greater than 
    1% with 95% confidence. You have no idea what to expect for $p$. How many 
    people would you have to sample to ensure that you are within the 
    guidelines?\
    *Hint:* Refer to your plot of the relationship between $p$ and margin of 
    error. This question does not require using the dataset.
