---
title: "Inference for Means II"
output:
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
library(knitr)
options(digits=3)
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(oilabs)
library(openintro)
```

## Naive analysis {.build}

Consider a data set containing the IQs of 36 men and the IQs of 36 women. Can use
this data to test the following?

$$
H_0: \mu_{M} - \mu_{F} = 0 \\
H_A: \mu_{M} - \mu_{F} \ne 0
$$

```{r echo = FALSE}
d <- data.frame(IQ = c(gifted$fatheriq, gifted$motheriq),
                sex = rep(c("male", "female"), each = nrow(gifted)))
set.seed(184)
d <- d[sample(1:nrow(d)), ]
head(d)
```


## {.smaller}

```{r}
(ds <- d %>%
  group_by(sex) %>%
  summarize(mean = mean(IQ),
            s = sd(IQ),
            n = n()))
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3}
qplot(x = IQ, data = d, geom = "bar", facets = ~ sex, fill = I("linen"), col = I("darkseagreen"))
```


## Two sample t-test {.build}

- We have a point estimate

```{r}
diff(ds$mean)
```

- We can calculate a standard error

```{r}
sqrt(ds$s[1]^2/sqrt(ds$n[1]) + ds$s[2]^2/sqrt(ds$n[2]))
```

- We can calculate the df

```{r}
min(ds$n[1] - 1, ds$n[2] - 1)
```


## Two sample t-test (cont.) {.build}

- But we need to check conditions
    - Nearly normal populations (barplots looked OK)
    - Independent observations


## Original Data

Data were collected from schools in a large city on a set of thirty-six children
who were identified as gifted children soon after they reached the age of four. 

```{r}
head(gifted)
```


## Paired data

If there is a natural pairing between observations in two groups of size n, it 
can make more sense to analyze them as a single sample of n differences.

```{r}
gifted %>%
  mutate(diff = fatheriq - motheriq) %>%
  select(fatheriq, motheriq, diff)
```


## Paired t-test {.build}

$$
H_0: \mu_{diff} = 0 \\
H_A: \mu_{diff} \ne 0
$$

### Check conditions
1. Independent observations
2. Nearly normal population

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3}
g <- gifted %>%
  mutate(diff = fatheriq - motheriq)
qplot(x = diff, data = g, geom = "density",fill = I("linen"), col = I("darkseagreen"))
```


## Paired t-test (cont.) {.build}

- Compute a test statistic

```{r}
(gs <- gifted %>%
  mutate(diff = fatheriq - motheriq) %>%
  summarize(mean = mean(diff), s = sd(diff), n = n()))
(t_obs <- (gs$mean - 0)/(gs$s/sqrt(gs$n)))
```

- $df = n - 1$


## Paired compared {.build}

```{r}
gs$s/sqrt(gs$n)
sqrt(ds$s[1]^2/sqrt(ds$n[1]) + ds$s[2]^2/sqrt(ds$n[2]))
```

While the point estimate is the same in the paired and independent tests, if
the data is paired, the dependency leads to a smaller SE.

This principle is widely used in experiment design, e.g. pre- and post-test.