---
title: "Hypothesis Testing II"
output:
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
library(knitr)
options(digits=2)
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```


# Simulation


## {.flexbox .vcenter}

Randomization

vs. 

Simulation


## The procedure {.build}

```{r prelim, echo=FALSE, message=FALSE}
library(ggplot2)
set.seed(53)
```

1. Let a coin flip represent selecting a random American. Heads = in favor.
2. Flip a coin 75 times and compute the proportion of heads.
3. Repeat step 2 many many times, logging the sample proportions

```{r sim, message=FALSE, warning=FALSE}
library(mosaic)
p_hats <- do(10000) * rflip(n = 75)
head(p_hats)

set.seed(24)
poll <- data.frame(person_id = 1:75,
                   favor = sample(rep(c("Yes", "No"), times = c(50, 25))))
```

```{r eval = FALSE, echo = FALSE}
library(infer)
d <- poll %>%
  specify(response = favor) %>%
  hypothesize(null = "point", p = c("Yes" = .50)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop", success = "Yes")

```


## The Hypotheses {.build}

Let $p$ be the true proportion of Americans who favor same-sex marriage.

$$H_0: p = 0.5$$

$$H_A: p \ne 0.5$$


## The Data

The *observed test statistic* was

$$\hat{p} = 0.66$$


## The Null Distribution

```{r dist, warning=FALSE, message=FALSE}
qplot(x = prop, data = p_hats, geom = "histogram", 
      binwidth = .0134, fill = I("white"), col = I("darkgreen"))
```


## The Null Distribution

```{r dist2, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
p_hats <- 
  p_hats %>%
  mutate(in_tail = ifelse(prop > .66 | prop < (1 - .66),
                          TRUE, FALSE))
qplot(x = prop, data = p_hats, geom = "histogram", fill = in_tail, 
      binwidth = .0134, fill = I("white"), col = I("darkgreen")) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("white", "darkgreen")) +
  geom_vline(xintercept = .66, col = "goldenrod")
```

```{r, eval=FALSE, echo=FALSE}
mean(p_hats$in_tail)
```

$$p.val \approx 0.006$$


## The decision {.build}

$$ \alpha = .05; \quad p.val \approx .006 $$

Since

$$ p.val < \alpha$$

we find the data is inconsistent with our model, aka, we reject the null hypothesis.


#


## Ways to find a Null Distribution {.flexbox .vcenter .build}

1. Randomization
2. Simulation
3. Probability Theory


## Probability Theory {.build}

Let $X$ be the total number of people in a sample of size 75 that favor same-sex
marriage if the true population proportion that favor is 0.5.

$x_{obs} = 75 \times 0.66 = 50$

What is $P(X > x_{obs})$?

$$ X \sim Binom(n = 75, p = .5) $$


## The Null Distribution

```{r, echo=FALSE, eval=TRUE}
x1  <- 0:75
df <- data.frame(x = x1, y = dbinom(x1, 75, 0.5))
qplot(x, y, data = df) + geom_bar(stat = "identity", col = "darkgreen", fill = "white")
#(1 - pbinom(50, 75, .5)) * 2
```

$$p.val = 0.002$$



