---
title: "Inference for Categorical Data"
output:
  ioslides_presentation:
    incremental: true
---


```{r setup, include=FALSE}
library(knitr)
options(digits=3)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(oilabs)
library(infer)
data(atheism)
data(millenials)
set.seed(358)
```


## Millennials and Marriage {.build}

In the national debate on same-sex marriage, it is commonly stated that half of all americans favor same-sex marriage. In 2014, Pew research conducted a poll of millennials (americans born after 1980) and found that 66% answered yes when asked: “Do you favor same-sex marriage?” The poll was a random sample of 75 millennials. Does this poll provide convincing evidence that the opinion of millennials is different from those of americans at large?

```{r}
head(millenials)
```


## Bootstrapping p-hat I {.build.smaller}

```{r}
millenials %>%
  specify(response = response) %>%
  generate(reps = 100, type = "bootstrap")
```

## Bootstrapping p-hat II {.build.smaller}

```{r}
millenials %>%
  specify(response = response) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop", success = "favor")
```

## Bootstrapping p-hat III {.build .smaller}

```{r}
millenials %>%
  specify(response = response) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop", success = "favor") %>%
  visualize()
```

## Bootstrapping p-hat III {.build.smaller}

```{r}
boot_se <- millenials %>%
  specify(response = response) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop", success = "favor") %>%
  summarize(se = sd(stat)) %>%
  as.numeric()
boot_se
```

## Constructing a CI {.build}

$$ \hat{p} \pm 1.96 \times SE $$
```{r}
p_hat <- millenials %>%
  summarize(p = mean(response == "favor")) %>%
  as.numeric()
c(p_hat - 1.96 * boot_se, p_hat + 1.96 * boot_se)
```

$$ .67 \pm 1.96 \times .057$$

# Normal Approximation Method

## Checking Conditions {.build}
  
$\hat{p} \sim N(\mu = p, \sigma = \sqrt{\frac{p(1-p)}{n}})$ if

1. Observations are independent
2. The number of observed successes and failures is more than 10.

$$
n\hat{p} \ge 10 \\
n(1 - \hat{p}) \ge 10
$$

## Question {.build}

We are given that $n = 75, \hat{p} = 0.67$. Which of the
below is the correct calculation of the 95% confidence interval?

1. $0.67 \pm 1.96 \sqrt{(.67 \times 0.33)/75}$
2. $0.67 \pm 1.65 \sqrt{(.67 \times 0.33)/75}$
3. $0.67 \pm 1.96 ((.67 \times 0.33)/\sqrt{75})$
4. $67 \pm 1.96 \sqrt{(67 \times 33)/75}$


## Constructing a CI {.build .smaller}


```{r construct}
nrow(millenials) * p_hat
nrow(millenials) * (1 - p_hat)
SE <- sqrt((p_hat * (1 - p_hat)) / nrow(millenials))
z_star <- qnorm(.025) # for a 95% CI
z_star
MoE <- z_star * SE
c(p_hat - MoE, p_hat + MoE)
```


## Choosing between methods {.build}

### Bootstrap SE

- Must have sufficiently large sample (n > 30)
- Can be calculated for any statistic

### Normal approximation

- Must satisfy assumptions (independence, sample size)
- Most commonly used (still)

# Interpreting a confidence interval
